### 2024-02-04 README.Rmd
indents and bulleting of readme

<!-- badges: start -->
<!-- badges: end -->

The goal of `sfislands` is to make it easier to deal with geographic datasets which contain islands. These do not have to be "literal" islands but any situation where discontiguous geographical units are present. Such a situation can lead to two issues. Firstly, if unaddressed, the presence of such islands or exclaves can make certain types of contiguity-based modelling impossible. Secondly, just because two areas are separated by, say, a body of water, this does not mean that they are necessarily independent. The package offers solutions to allow for the inclusion or exclusion of these units within an uncomplicated workflow.

>>>>

<!-- badges: start -->

<!-- badges: end -->

The goal of `sfislands` is to make it easier to deal with geographic datasets which contain islands.

-   These do not have to be "literal" islands but any situation where discontiguous geographical units are present.

Such a situation can lead to two issues.

-   Firstly, if unaddressed, the presence of such islands or exclaves can make certain types of contiguity-based modelling impossible.

-   Secondly, just because two areas are separated by, say, a body of water, this does not mean that they are necessarily independent.

This package offers solutions to allow for the inclusion or exclusion of these units within an uncomplicated workflow.
